---
title: "Plots - Relationship with Gamble Decisions"
author: "Johnny Lau"
date: "24/03/2020"
output: html_document
---
# Result plots markdown {.tabset}  
The RainCloudPlot function used here was created by Allen et al (2019).  
DOI: 10.12688/wellcomeopenres.15191.1  
It can be downloaded here (https://github.com/RainCloudPlots/RainCloudPlots)

```{r, include=FALSE}
#{r setup, include=FALSE, cache=TRUE, echo=FALSE}

#remove all existing variables in the environment
rm(list=ls())

current_dir = "C:/Users/DrJKLau/Desktop/BehData_curi-fmri_osf"
setwd(current_dir)

```

## Setup and data prep 
Load packages and data

```{r load packages and data}

require(pacman)

# Read into the data for analysis
df <- read.csv(file = 'data1_initial_behav.csv', header=TRUE, sep=",")

knitr::opts_chunk$set(cache=T)

# check if a package is installed and then load it
p_load(ggplot2)
p_load(cowplot)
p_load(dplyr)
p_load(readr)
p_load(lme4)
p_load(kableExtra)
p_load(sjPlot)


# Read R code from another file
source("R_rainclouds.R")  
#this R_rainclouds plot function is downloaded from https://github.com/RainCloudPlots/RainCloudPlots


```

## RainCloudPlot {.tabset .active}
### Preparing a theme 
Setting up a theme for the plot (Relationship beween Stimulus Rating and Gamble Decisions)
```{r plot design}


raincloud_theme <- theme(
  #text = element_text(size = 10),
  axis.title.x = element_blank(), 
  axis.title.y = element_text(size="10", face="bold", color="black", margin = margin(t = 0, r = 4)), 
  axis.text.x = element_text(size = 9, face="bold", margin = margin(t = 10, r = 0, b = 0, l = 15), colour = 'black'),
  axis.text.y = element_text(size = 9,  margin = margin(t = 0, r = 5, b = 0, l = 0), colour = 'black'),
  legend.title=element_text(size=10),
  legend.text=element_text(size=8),
  legend.position = 'bottom',   
  #plot.title = element_text(lineheight=.8, face="bold", size = 16),
  panel.border = element_blank(),
  panel.background = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(), 
  axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
  axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
  axis.ticks.length = unit(0, "cm")) 


```

### Data wrangling
Re-structuring data for plotting
```{r data wrangling}

# Using 'aggregate', split data into subsets computing summary statistics for each
  # raw_rate: raw rating of curiosity and desirability for food
  # category: food or magic (or trivia in one of the fMRI experiments)
  # choice/decision:  1 for accepted; 0 for rejected
agg_ppt_data <- aggregate(raw_rate~participant+category+choice, data=df, FUN=mean)

# re-label choice/decision options
agg_ppt_data["Decision"] <-NA
agg_ppt_data$Decision[agg_ppt_data$choice==0] <- "Reject"
agg_ppt_data$Decision[agg_ppt_data$choice==1] <- "Accept"


# compile Mean, SD, & SE of ratings across participants into a DataFrame
rst_m <- aggregate(raw_rate~category+choice, data=df, FUN=mean)
names(rst_m)[3]<- "group_mean_rate"

rst_sd <-  aggregate(raw_rate~category+choice, data=df, FUN=sd)  
names(rst_sd)[3]<- "sd_rate"
rst <- merge(rst_m, rst_sd, by = c("category", "choice"))


rst["se_rate"] <- rst$sd_rate/sqrt(length(unique(df$participant)))

# re-label choice/decision options
rst["Decision"] <-NA
rst$Decision[rst$choice==0] <- "Reject"
rst$Decision[rst$choice==1] <- "Accept"

# also compute the ymin and ymax of the error bars using SE of ratings
rst$ymin = with(rst, group_mean_rate - se_rate)
rst$ymax = with(rst, group_mean_rate + se_rate)




```

### Plotting  {.active}
```{r, message=FALSE}

#use ggplot and R_rainclouds.script (esp 'geom_flat_violin' function) for plotting
g_cloudplot <- ggplot() + 
  geom_flat_violin(data = agg_ppt_data, aes(y = raw_rate, x = category, fill=Decision), position = position_nudge(x = .2, y = 0), alpha = .6, colour=FALSE, show.legend = FALSE) +
  # add data-points (average ppt rating of each participant)
  geom_point(data=agg_ppt_data, aes(y = raw_rate, x = category, color = Decision), position = position_jitter(width=.1),size = 1.5, alpha = 0.8, show.legend = FALSE, shape=16) +
  # add the summary scores (average rating across participants for each condition )
  geom_pointrange (data=rst, aes(y = group_mean_rate, x = category, ymin= ymin, ymax= ymax, color=Decision), shape=16, size=1.2, position = position_dodge(width=0.1)) + 
  
  # adjust other plot features
  raincloud_theme + 
  scale_x_discrete(labels=c("Curiosity","Food Desirability")) +
  ylim(0,7) +
  labs(fill = "Decision") +
  scale_y_continuous(name="Acceptance Rate")

g_cloudplot

# Try the following line to save the plot as an image
#ggsave("RCP_initialbeh.jpeg", width = 140, height = 180, units = "mm", dpi=300, limitsize=FALSE)

```



## Logistic function (Sigmoid curve) {.tabset}
### Data preparation & GLMM
Some data re-coding & (Generalised) Linear Mixed-effects Modelling 
```{r preparation & GLMM}

#ctrd_prob <- -(df$re_prob)

#effect coding of the Category variable
df$cond <- (as.numeric(df$category == "curiosity") - 0.5)*2



#modelling the curiosity trials separately
df_curi <- subset(df, category=="curiosity")

ctrd_prob <- -(df_curi$re_prob) #recode the presented (win/loss) outcome probability so that it reflects the prospective chance of shock

glmm_curi<- glmer(choice ~ ctrd_prob*ctrd_rate
        + (1 | participant) + (-1 + ctrd_rate| participant) 
        + (-1 + ctrd_prob| participant), 
        data = df_curi, family = binomial (link= "logit"))
curi_summary <- summary(glmm_curi)

#curi_summary

tab_model(glmm_curi, string.est="Estimate", transform=NULL, show.stat=TRUE, show.se=TRUE, show.df=TRUE)



#modelling the food trials separately
df_food <- subset(df, category=="food")

ctrd_prob <- -(df_food$re_prob) #recode the presented (win/loss) outcome probability so that it reflects the prospective chance of shock

glmm_food<- glmer(choice ~ ctrd_prob*ctrd_rate
                  + (1 | participant) + (-1 + ctrd_rate| participant) 
                  + (-1 + ctrd_prob| participant),
                 data = df_food, family = binomial (link= "logit"))
food_summary <- summary(glmm_food)

#food_summary

tab_model(glmm_food, string.est="Estimate", transform=NULL, show.stat=TRUE, show.se=TRUE, show.df=TRUE)

```


### Data Wrangling
Preparing modelled data for plotting logistic function
```{r modelled data & wrangling}


#Generate a series of continuous x-variable (for plotting later)
x <- seq(-5,5,length.out=100)


##To retrieve Estimates (beta coefficients) of various variables from GLMM model for data modelling
#Information trials
cintercept <- curi_summary$coefficients["(Intercept)", "Estimate"]
cbeta_prob <-  curi_summary$coefficients["ctrd_prob", "Estimate"]
cbeta_rate <- curi_summary$coefficients["ctrd_rate", "Estimate"]

#the modelled y-cooridinate data computed with GLMM model coefficients
y_cmean <- 1/(1+exp(-1*(cintercept + cbeta_prob*x)))

##To retrieve Estimates (beta coefficients) of various variables from GLMM model for data modelling
#Food trials
fintercept <- food_summary$coefficients["(Intercept)", "Estimate"]
fbeta_prob <- food_summary$coefficients["ctrd_prob", "Estimate"]
fbeta_rate <- food_summary$coefficients["ctrd_rate", "Estimate"]

#the modelled y-cooridinate data computed with GLMM model coefficients
y_fmean <- 1/(1+exp(-1*(fintercept + fbeta_prob*x)))


#compile all (modelled) datapoints into a DataFrame for plotting with ggplot
df_plot <- data.frame(x_var=x, y_cmean=y_cmean, y_fmean=y_fmean)



##additional data re-structuring: for plotting distribution of participants' raw data in the same graph

#to summarise data so that (for each subject) the average acceptance rate is computed at each (shock) probability level
food_selcols <- data.frame(df_food$participant, df_food$re_prob, df_food$choice) 
names(food_selcols)[c(1,2,3)] <- c("participant","re_prob","choice")

##recoding reward outcome probability to shock probability 
food_selcols["ShockProb"] <- NA
food_selcols$ShockProb[food_selcols$re_prob== -2] <- 4
food_selcols$ShockProb[food_selcols$re_prob== -1] <- 2
food_selcols$ShockProb[food_selcols$re_prob== 0] <- 0
food_selcols$ShockProb[food_selcols$re_prob== 1] <- -2
food_selcols$ShockProb[food_selcols$re_prob== 2] <- -4

efg<- aggregate(choice~participant+ShockProb, data=food_selcols, FUN=function(x) avg_accept=mean(x))
names(efg)[3]<-"avg_ppt_choice"


#to summarise data so that (for each subject) the average acceptance rate is computed at each (shock) probability level
cur_selcols <- data.frame(df_curi$participant, df_curi$re_prob, df_curi$choice) 
names(cur_selcols)[c(1,2,3)] <- c("participant","re_prob","choice")


##recoding reward outcome probability to shock probability 
cur_selcols["ShockProb"] <- NA
cur_selcols$ShockProb[cur_selcols$re_prob== -2] <- 4
cur_selcols$ShockProb[cur_selcols$re_prob== -1] <- 2
cur_selcols$ShockProb[cur_selcols$re_prob== 0] <- 0
cur_selcols$ShockProb[cur_selcols$re_prob== 1] <- -2
cur_selcols$ShockProb[cur_selcols$re_prob== 2] <- -4
abc<- aggregate(choice~participant+ShockProb, data=cur_selcols, FUN=function(x) avg_accept=mean(x))
names(abc)[3]<-"avg_ppt_choice"


```


### Plotting 
```{r logistic plotting}

# plot the modelled curves (separately for curiosity condition and food condition)
sigplot<- ggplot(data=df_plot, aes(x=x_var)) + 
  geom_line(aes(y=y_cmean, color='curiosity'), size=1, linetype="solid")  +
    geom_line(aes(y=y_fmean, color='food'), size=1, linetype="solid") +
  scale_color_manual(name="Category", values= c(food = "red", curiosity = "blue"))
  
# add and adjust graph elements
axis.title.bold <- element_text(face="bold", size="12", color="black")
axis.text.bold <- element_text(face="bold", size="12", color="black")

sigplot <- sigplot + scale_x_continuous(name="Probability of Shock (%)", breaks=c(-4,-2,0,2,4), labels=c("-4"="16.7%", "-2"="33.3%", "0"="50%", "2"="66.7%", "4"="83.3%")) + 
  scale_y_continuous(name="Acceptance Rate", breaks=c(0, 0.5, 1)) +
  ggtitle("Effect of Prospective Shock Probability on 'Accept' Decision") +
  theme_classic() +
  theme(axis.title=axis.title.bold, axis.text =axis.text.bold) #plot.title = title.align, 


# also plot the raw data-points (from each participant at each probabilty level) on the graph
sigplot <- sigplot + geom_point(data = efg, mapping = aes(x = ShockProb, y = avg_ppt_choice), shape=1, position=position_jitter(h=0.03,w=0.18), color="blue") +
  geom_point(data = abc, mapping = aes(x = ShockProb, y = avg_ppt_choice), shape=1, position=position_jitter(h=0.03,w=0.18), color="red")



sigplot

```
