---
title: "Plots - Relationship with Gamble Decisions"
author: "Johnny Lau"
date: "24/03/2020"
output: html_document
---
# Result plots markdown {.tabset}  
The RainCloudPlot function used here was created by Allen et al (2019).  
DOI: 10.12688/wellcomeopenres.15191.1  
It can be downloaded here (https://github.com/RainCloudPlots/RainCloudPlots)

```{r, include=FALSE}
#remove all existing variables in the environment
rm(list=ls())


```

## Setup and data prep 
Load packages and data

```{r load packages and data}

require(pacman)

knitr::opts_chunk$set(cache=T)

##uncomment this part to use osfr package to get access and download data from OSF

#p_load(osfr)
#
#curi_project <- osf_retrieve_node("https://osf.io/mafe3/") # access OSF project
#
#osf_retrieve_node("mafe3") %>%
#  osf_ls_files() %>%
#  osf_download() # download data to your current directory 
## to check your current directory, use getwd()


# check if a package is installed and then load it
p_load(ggplot2)
p_load(cowplot)
p_load(dplyr)
p_load(readr)
p_load(lme4)
p_load(kableExtra)
p_load(sjPlot)


# Read R code from another file
source("R_rainclouds.R")  
#this R_rainclouds plot function is downloaded from https://github.com/RainCloudPlots/RainCloudPlots


```

## RainCloudPlot {.tabset .active}
### Preparing a theme 
Setting up a theme for the plot (Relationship beween Stimulus Rating and Gamble Decisions)
```{r plot design}


raincloud_theme <- theme(
  #text = element_text(size = 10),
  axis.title.x = element_blank(), 
  axis.title.y = element_text(size="10", face="bold", color="black", margin = margin(t = 0, r = 4)), 
  axis.text.x = element_text(size = 9, face="bold", margin = margin(t = 10, r = 0, b = 0, l = 15), colour = 'black'),
  axis.text.y = element_text(size = 9,  margin = margin(t = 0, r = 5, b = 0, l = 0), colour = 'black'),
  legend.title=element_text(size=10),
  legend.text=element_text(size=8),
  legend.position = 'bottom',   
  #plot.title = element_text(lineheight=.8, face="bold", size = 16),
  panel.border = element_blank(),
  panel.background = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(), 
  axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
  axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
  axis.ticks.length = unit(0, "cm")) 


```

### Data wrangling
Re-structuring data for plotting
```{r data wrangling}

# Read into the data for analysis
read_csv <- function(df) {
  read.csv(file = df, header=TRUE, sep=",")}

df <- read_csv('Data files/data1_initial_behav.csv')


# Using 'aggregate' function, split data into subsets computing summary statistics for each
  # raw_rate: raw rating of curiosity and desirability for food
  # category: food or magic (or trivia in one of the fMRI experiments)
  # choice/decision:  1 for accepted; 0 for rejected

calc_agg_ppt <- function(df){
  agg_ppt_data <- aggregate(raw_rate~participant+category+choice, data=df, FUN=mean)

  # re-label choice/decision options
  agg_ppt_data["Decision"] <-NA
  agg_ppt_data$Decision[agg_ppt_data$choice==0] <- "Reject"
  agg_ppt_data$Decision[agg_ppt_data$choice==1] <- "Accept"
  
  return(agg_ppt_data)
}


calc_avg_datapoint <- function(df){
  # compile Mean, SD, & SE of ratings across participants into a DataFrame
  avg_data_m <- aggregate(raw_rate~category+choice, data=df, FUN=mean)
  names(avg_data_m)[3]<- "group_mean_rate"

  avg_data_sd <-  aggregate(raw_rate~category+choice, data=df, FUN=sd)  
  names(avg_data_sd)[3]<- "sd_rate"
  avg_data <- merge(avg_data_m, avg_data_sd, by = c("category", "choice"))
  
  
  avg_data["se_rate"] <- avg_data$sd_rate/sqrt(length(unique(df$participant)))
  
  # re-label choice/decision options
  avg_data["Decision"] <-NA
  avg_data$Decision[avg_data$choice==0] <- "Reject"
  avg_data$Decision[avg_data$choice==1] <- "Accept"
  
  # also compute the ymin and ymax of the error bars using SE of ratings
  avg_data$ymin = with(avg_data, group_mean_rate - se_rate)
  avg_data$ymax = with(avg_data, group_mean_rate + se_rate)
  
  return(avg_data)
}

agg_ppt_data = calc_agg_ppt(df)
avg_data = calc_avg_datapoint(df)


```

### Plotting  {.active}
```{r, message=FALSE}

raincloudplot <- function(ppt_data, avg_data){
  #use ggplot and R_rainclouds.script (esp 'geom_flat_violin' function) for   plotting
  ggplot() + 
    geom_flat_violin(data = ppt_data, aes(y = raw_rate, x = category,   fill=Decision), position = position_nudge(x = .2, y = 0), alpha = .6,   colour=FALSE, show.legend = FALSE) +
    # add data-points (average ppt rating of each participant)
    geom_point(data= ppt_data, aes(y = raw_rate, x = category, color =   Decision), position = position_jitter(width=.1),size = 1.5, alpha = 0.8,   show.legend = FALSE, shape=16) +
    # add the summary scores (average rating across participants for each condition   )
    geom_pointrange (data=avg_data, aes(y = group_mean_rate, x = category, ymin=   ymin, ymax= ymax, color=Decision), shape=16, size=1.2, position =   position_dodge(width=0.1)) + 
    
    # adjust other plot features
    raincloud_theme + 
    scale_x_discrete(labels=c("Curiosity","Food Desirability")) +
    ylim(0,7) +
    labs(fill = "Decision") +
    scale_y_continuous(name="Stimulus Rating")
  
}


g_rcp <- raincloudplot(agg_ppt_data, avg_data)

g_rcp

# Try the following line to save the plot as an image
#ggsave("RCP_initialbeh.jpeg", width = 140, height = 180, units = "mm", dpi=300, limitsize=FALSE)

```



## Logistic function (Sigmoid curve) {.tabset}
### Data preparation & GLMM
Some data re-coding & (Generalised) Linear Mixed-effects Modelling 
```{r preparation & GLMM}

glm_curi <- function(df){
  #modelling the curiosity trials separately
  df_curi <- subset(df, category=="curiosity")
  
  ctrd_prob <- -(df_curi$re_prob) #recode the presented (win/loss) outcome   probability so that it reflects the prospective chance of shock
  
  glmm_curi<- glmer(choice ~ ctrd_prob*ctrd_rate
          + (1 | participant) + (-1 + ctrd_rate| participant) 
          + (-1 + ctrd_prob| participant), 
          data = df_curi, family = binomial (link= "logit"))
  curi_summary <- summary(glmm_curi)
  
  
  tab_model(glmm_curi, string.est="Estimate", transform=NULL, show.stat=TRUE, show.se=TRUE, show.df=TRUE)
 
  return(curi_summary)
}

curi_summary <- glm_curi(df)



glm_food <- function(df){
  #modelling the food trials separately
  df_food <- subset(df, category=="food")
  
  ctrd_prob <- -(df_food$re_prob) #recode the presented (win/loss) outcome   probability so that it reflects the prospective chance of shock
  
  glmm_food<- glmer(choice ~ ctrd_prob*ctrd_rate
                    + (1 | participant) + (-1 + ctrd_rate| participant) 
                    + (-1 + ctrd_prob| participant),
                   data = df_food, family = binomial (link= "logit"))
  food_summary <- summary(glmm_food)
  
  tab_model(glmm_food, string.est="Estimate", transform=NULL, show.stat=TRUE, show.se=TRUE, show.df=TRUE)
  
  return(food_summary)
}

food_summary <- glm_food(df)


```


### Data Wrangling
Preparing modelled data for plotting logistic function
```{r modelled data & wrangling}

dp_modelled <- function(curi_summary, food_summary){
#Generate a series of continuous x-variable (for plotting later)
  x <- seq(-5,5,length.out=100)
  
  ##To retrieve Estimates (beta coefficients) of various variables from GLMM model   for data modelling
  #Information trials
  cintercept <- curi_summary$coefficients["(Intercept)", "Estimate"]
  cbeta_prob <-  curi_summary$coefficients["ctrd_prob", "Estimate"]
  cbeta_rate <- curi_summary$coefficients["ctrd_rate", "Estimate"]
  
  #the modelled y-cooridinate data computed with GLMM model coefficients
  y_cmean <- 1/(1+exp(-1*(cintercept + cbeta_prob*x)))
  
  ##To retrieve Estimates (beta coefficients) of various variables from GLMM model   for data modelling
  #Food trials
  fintercept <- food_summary$coefficients["(Intercept)", "Estimate"]
  fbeta_prob <- food_summary$coefficients["ctrd_prob", "Estimate"]
  fbeta_rate <- food_summary$coefficients["ctrd_rate", "Estimate"]
  
  #the modelled y-cooridinate data computed with GLMM model coefficients
  y_fmean <- 1/(1+exp(-1*(fintercept + fbeta_prob*x)))
  
  
  #compile all (modelled) datapoints into a DataFrame for plotting with ggplot
  df_plotdata <- data.frame(x_var=x, y_cmean=y_cmean, y_fmean=y_fmean)
  
  df_plotdata
}


df_plotdata <- dp_modelled(curi_summary, food_summary)



##additional data re-structuring: for plotting distribution of participants' raw data in the same graph

ppt_foodprob_data <- function(df){
  #to summarise data so that (for each subject) the average acceptance rate is computed at each (shock) probability level
  df_food <- subset(df, category=="food")
  
  food_selcols <- data.frame(df_food$participant, df_food$re_prob, df_food$choice) 
  names(food_selcols)[c(1,2,3)] <- c("participant","re_prob","choice")
  
  ##recoding reward outcome probability to shock probability 
  food_selcols["ShockProb"] <- NA
  food_selcols$ShockProb[food_selcols$re_prob== -2] <- 4
  food_selcols$ShockProb[food_selcols$re_prob== -1] <- 2
  food_selcols$ShockProb[food_selcols$re_prob== 0] <- 0
  food_selcols$ShockProb[food_selcols$re_prob== 1] <- -2
  food_selcols$ShockProb[food_selcols$re_prob== 2] <- -4
  
  efg<- aggregate(choice~participant+ShockProb, data=food_selcols, FUN=function(x) avg_accept=mean(x))
  names(efg)[3]<-"avg_ppt_choice"
  
  efg
}
  

ppt_curiprob_data <- function(df){
  #to summarise data so that (for each subject) the average acceptance rate is computed at each (shock) probability level
  df_curi <- subset(df, category=="curiosity")
  
  cur_selcols <- data.frame(df_curi$participant, df_curi$re_prob, df_curi$choice) 
  names(cur_selcols)[c(1,2,3)] <- c("participant","re_prob","choice")
  
  
  ##recoding reward outcome probability to shock probability 
  cur_selcols["ShockProb"] <- NA
  cur_selcols$ShockProb[cur_selcols$re_prob== -2] <- 4
  cur_selcols$ShockProb[cur_selcols$re_prob== -1] <- 2
  cur_selcols$ShockProb[cur_selcols$re_prob== 0] <- 0
  cur_selcols$ShockProb[cur_selcols$re_prob== 1] <- -2
  cur_selcols$ShockProb[cur_selcols$re_prob== 2] <- -4
  abc<- aggregate(choice~participant+ShockProb, data=cur_selcols, FUN=function(x) avg_accept=mean(x))
  names(abc)[3]<-"avg_ppt_choice"
  
  abc
}


avg_ppt_foodprob <- ppt_foodprob_data(df)
avg_ppt_curiprob <- ppt_curiprob_data(df)


```


### Plotting 
```{r logistic plotting}

sigmoidplot <- function(df_plotdata, ppt_foodprob_data, ppt_curiprob_data){
  # plot the modelled curves (separately for curiosity condition and food   condition)
  sigplot<- ggplot(data=df_plotdata, aes(x=x_var)) + 
    geom_line(aes(y=y_cmean, color='curiosity'), size=1, linetype="solid")  +
      geom_line(aes(y=y_fmean, color='food'), size=1, linetype="solid") +
    scale_color_manual(name="Category", values= c(food = "red", curiosity =   "blue"))
    
  # add and adjust graph elements
  axis.title.bold <- element_text(face="bold", size="12", color="black")
  axis.text.bold <- element_text(face="bold", size="12", color="black")
  
  sigplot <- sigplot + scale_x_continuous(name="Probability of Shock (%)",   breaks=c(-4,-2,0,2,4), labels=c("-4"="16.7%", "-2"="33.3%", "0"="50%",   "2"="66.7%", "4"="83.3%")) + 
    scale_y_continuous(name="Acceptance Rate", breaks=c(0, 0.5, 1)) +
    ggtitle("Relationship between Prospective Shock Probability and Gamble Decision") +
    theme_classic() +
    theme(axis.title=axis.title.bold, axis.text =axis.text.bold) +
  
  
  # also plot the raw data-points (from each participant at each probabilty level)   on the graph
    geom_point(data = ppt_foodprob_data, mapping = aes(x =   ShockProb, y = avg_ppt_choice), shape=1, position=position_jitter(h=0.03,w=0.18),   color="blue") +
    geom_point(data = ppt_curiprob_data, mapping = aes(x = ShockProb, y =   avg_ppt_choice), shape=1, position=position_jitter(h=0.03,w=0.18), color="red")

sigplot
}

g_sp <- sigmoidplot(df_plotdata, avg_ppt_foodprob, avg_ppt_curiprob)

g_sp

```
